Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-11-22 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Cropped PDF

## Parametric \& Non-Parametric Shannon Entropy

The parametric representation of Shannon entropy for a system described by a continuous random variable is:
\begin{equation}
  \label{E:entropy2}
  H_(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
\end{equation}
here, $f(\cdot)$ is the probability density function that characterizes the distribution of the real-valued random variable $Z$.

@@

```{r 3d_GIO, fig.align="center",  out.width = "120%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
```
As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.

>>>>

## The Shannon Entropy
The parametric representation of Shannon entropy for a system described by a continuous random variable is:
\begin{equation}
  \label{E:entropy2}
  H_(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
\end{equation}
here, $f(\cdot)$ is the probability density function that characterizes the distribution of the real-valued random variable $Z$.

@@

```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
```
As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.

## Estimation of the Shannon Entropy
